---
output: github_document
bibliography: inst/REFERENCES.bib
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# evoarchdata

The goal of evoarchdata is to make easily available some important artefact datasets from archaeological studies of cultural evolution. The motivation for this package is to make it easier to teach and study cultural evolution in the archaeological record. 

## Installation

You can install the development version of evoarchdata from GitHub with:

``` r
if (!require(devtools)) install.packages("devtools")
install_github("benmarwick/evoarchdata")
```

## Datasets

Here's a summary of the datasets currently in this package:

```{r}
tbl_of_data <- vcdExtra::datasets("evoarchdata")
knitr::kable(tbl_of_data)
```

# Use

To use a dataset in your R session, you can load it like this:

```{r}
library(evoarchdata)
data(ceramics_lbk_merzbach)

# and then take a look at the data
ceramics_lbk_merzbach
```

If you use any of these datasets, you must cite the original publication, listed below. 

The datasets are made available here for fair use in teaching and research. All datasets are copyright of the original author or publisher, except `ceramics_lbk_merzbach` which is distributed by Crema et al (2016) under the terms of the [Creative Commons CC BY license](https://creativecommons.org/licenses/), which permits unrestricted use, distribution, and reproduction in any medium, provided the original work is properly cited. 

# Contributing

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.

# Bibliography
