---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# evoarchdata

The goal of evoarchdata is to make easily available some important artefact datasets from archaeological studies of cultural evolution. The motivation for this package is to make it easier to teach and study cultural evolution in the archaeological record. 

## Installation

You can install the development version of evoarchdata from GitHub with:

``` r
if (!require(devtools)) install.packages("devtools")
install_github("benmarwick/evoarchdata")
```

## Datasets

Here's a summary of the datasets currently in this package:

```{r}
tbl_of_data <- vcdExtra::datasets("evoarchdata")
knitr::kable(tbl_of_data)
```

Here's a preview of each dataset:

```{r}
# get an object referring to the datasets
d <- data(package = "evoarchdata")

# get names of the datasets
nm <- d$results[, "Item"]

# call the promised data into the environment
data(list = nm, package = "evoarchdata")

# print the first few rows of each dataset
lapply(mget(nm), head)
```

# Use

To use a dataset in your R session, you can load it like this:

```{r}
library(evoarchdata)
data(ceramics_lbk_merzbach)

# and then take a look at the data
ceramics_lbk_merzbach
```


If you use any of these datasets, you much cite the original publication, listed below. 

The datasets are made available here for fair use in teaching and research. All datasets are copyright of the original author or publisher, except `ceramics_lbk_merzbach` which is distributed by Crema et al (2016) under the terms of the [Creative Commons CC BY license](https://creativecommons.org/licenses/), which permits unrestricted use, distribution, and reproduction in any medium, provided the original work is properly cited. 

# References

Brantingham, P. J., & Perreault, C. (2010). Detecting the effects of selection and stochastic forces in archaeological assemblages. _Journal of Archaeological Science_, 37(12), 3211-3225. https://doi.org/10.1016/j.jas.2010.07.021

Braun, D. 1977. _Middle Woodland-Early Late Woodland Social Change in the Prehistoric Central Midwestern U.S._ Ph.D. dissertation, University of Michigan, University Microfilms, Ann Arbor.

Braun, D. 1985. Ceramic decorative diversity and Illinois Woodland regional integration. In _Decoding Prehistoric Ceramics_, edited by Ben A. Nelson, pp.128-153. Southern Illinois University Press Carbondale.

Crema, E.R., Edinborough, K., Kerig, T., Shennan, S.J., 2014. An Approximate Bayesian Computation approach for inferring patterns of cultural evolutionary change. _Journal of Archaeological Science_ 50, 160–170. https://doi.org/10.1016/j.jas.2014.07.014

Crema, E.R, Kandler, A., Shennan, S.J. 2016. "Revealing patterns of cultural transmission from frequency data: equilibrium and non-equilibrium assumptions." _Scientific Reports_ 6, 39122; https://doi.org/10.1038/srep39122 

Neiman, F.D., 1995. Stylistic Variation in Evolutionary Perspective: Inferences from Decorative Diversity and Interassemblage Distance in Illinois Woodland Ceramic Assemblages. _American Antiqity_ 60, 7–36. https://doi.org/10.2307/282074

Saintot, S. 1998 Les Armatures de Flèches en Silex de Chalain et de Clairvaux In _Gallia préhistoire_. Tome 40 (1998), pp. 204-241

Steele, J., Glatz, C., Kandler, A., 2010. Ceramic diversity, random copying, and tests for selectivity in ceramic production. _Journal of Archaeological Science_ 37, 1348–1358. https://doi.org/10.1016/j.jas.2009.12.039

# Contributing

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.

